Age-related changes in plant growth and traits

### 2015-05-21 results_growth.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

```{r, echo=FALSE, message=FALSE}
plot((total_weight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "total_weight"
xvar <- "PropH"

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "PropH"

@@

```{r, echo=FALSE, message=FALSE}
yvar <- "RGR"
xvar <- "PropH"

@@

```{r, echo=FALSE,message=FALSE}
plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
mod <- lm(change_shoot_area~change_basal_area*age*species,SummaryInd)
anova(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
```

@@

  abline(lmfits[[spp]])
}
```
###Diameter increase in shoots vs. whole plant
- The slope of the relationship lessens with age  
- There is quite a bit of noise in the relationship  
- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
```{r, echo=FALSE,message=FALSE}
plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
abline(0,1)

mod <- lm (change_shoot_diam ~ change_basal_diam*age,data=subset(SummaryInd, age>1.4))
summary(mod)
anova(mod)

plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
abline(0,1)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)

plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)

yvar <- "change_shoot_diam"
xvar <- "change_basal_diam"

>>>>

```{r, echo=FALSE, message=FALSE}
plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "total_weight"
xvar <- "prop_maxH"

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "prop_maxH"

@@

```{r, echo=FALSE, message=FALSE}
yvar <- "RGR"
xvar <- "prop_maxH"

@@

```{r, echo=FALSE,message=FALSE}
plot(growth_shoot_area~growth_stem_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
mod <- lm(growth_shoot_area~growth_stem_area*age*species,SummaryInd)
anova(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
```

@@

  abline(lmfits[[spp]])
}
```
###Diameter increase in shoots vs. whole plant
- The slope of the relationship lessens with age  
- There is quite a bit of noise in the relationship  
- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
```{r, echo=FALSE,message=FALSE}
plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
abline(0,1)

mod <- lm (growth_shoot_diam ~ growth_stem_diam*age,data=subset(SummaryInd, age>1.4))
summary(mod)
anova(mod)

plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
abline(0,1)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)

plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)

yvar <- "growth_shoot_diam"
xvar <- "growth_stem_diam"

### 2015-05-21 results_leaf_lifespan.rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

#PropH vs LL_death
- Have just plotted overall data, because no relationships across or within species; only GRSP has significant negative relationship and BOLE has significant positive relationship
```{r, echo=FALSE,message=FALSE}
plot((LL_death~PropH), data=subset(SummaryInd,LL_death<10), col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((PropH~log(age)), data=subset(SummaryInd), col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

>>>>

#prop_maxH vs LL_death
- Have just plotted overall data, because no relationships across or within species; only GRSP has significant negative relationship and BOLE has significant positive relationship
```{r, echo=FALSE,message=FALSE}
plot((LL_death~prop_maxH), data=subset(SummaryInd,LL_death<10), col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((prop_maxH~log(age)), data=subset(SummaryInd), col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```
